---
title: "R Notebook"
output: html_note0ook
---


```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = TRUE) 
```


Question: 
Today's worlld,capitalism is wellknow since most of the countirs ruled bycapitalis. However, it is worthy to understand the ideas behinds communism too. In order to understand communism, what aspect should we pay more attention to? In other words. We do not have time to read all 3 books. but through which key words can help shape the basic understandng of communism.(seperate by boo? why" length different)


where does the sentiments come from.

<center> <h2> #The Breif Introduction on 'Capitalism' and 'Communism'</h2> </center>
<br><br>

### Capitalism is defined as an economic system in which a country’s trade, industry, and profits are controlled only by private companies. The United States and most of the nations around the world are capitalist countries, but capitalism is not the only economic system available. Communism, on the other hand, advocating that goods are owned in common and are available to all as needed, means of production are owned communally.


*** 
> ## block quote 




```{r}
library(RColorBrewer)
library(tm)
library(wordcloud)
library(NLP)
library(tidyverse)
library(syuzhet)
```




##### Seperate datasets into: capitalism, communism, Communist_Manifesto, lenin, Capital

```{r}
docs =  read.csv("philosophy_data.csv",stringsAsFactors =  F) 

capitalism  =
  docs %>% filter(school  == "capitalism")
communism  =
  docs %>% filter(school  == "communism")
Communist_Manifesto  =
  docs %>% filter(title  == "The Communist Manifesto")
lenin  =
  docs %>% filter(title  == "Essential Works Of Lenin")
Capital  =
  docs %>% filter(title  == "Capital")

```

## See results overall from the entire dataset
```{r}

## data preprocessing

words = Corpus(VectorSource(docs$lemmatized_str))
words = tm_map(words, removeNumbers)
words = tm_map(words, removePunctuation)
words = tm_map(words, removeWords, c("the", "and", "PRON", stopwords("english"))) # Remove PRON 
words =  tm_map(words, stripWhitespace)

### Document matirx


words_dtm <- DocumentTermMatrix(words)
findFreqTerms(words_dtm, lowfreq = 10)


findFreqTerms(words_dtm, 50)

## wordcloud
freq = data.frame(sort(colSums(as.matrix(words_dtm)), decreasing=TRUE))
wordcloud(rownames(freq), freq[,1], max.words=50, colors=brewer.pal(1, "Dark2"))

```

# See Results from Captilism

```{r}
################################################ Capitalism ############################################################

## data preprocessing
words = Corpus(VectorSource(capitalism$lemmatized_str))
words = tm_map(words, removeNumbers)
words = tm_map(words, removePunctuation)
words = tm_map(words, removeWords, c("the", "and", "PRON", stopwords("english"))) # Remove PRON 
words = tm_map(words, removeWords, c("must", "however", "two", "one", "upon", "much", "every", "either", "must", "can","may","therefore","will", "good","great", stopwords("english")))
words =  tm_map(words, stripWhitespace)

### Document matrix1
words_dtm <- DocumentTermMatrix(words)
### Document matrix2
words_dtm_tfidf <- DocumentTermMatrix(words, control = list(weighting = weightTfIdf))
words_dtm_tfidf = removeSparseTerms(words_dtm_tfidf, 0.95)
inspect(words_dtm_tfidf[1,1:20])


## creating freq data frame
freq = data.frame(sort(colSums(as.matrix(words_dtm)), decreasing=TRUE))
table = data.frame(term = row.names(freq), frequency= freq)
colnames(table) = c('term', 'frequency')

# Bar chart
p<-ggplot(data= subset(table, frequency >1000), aes(x=reorder(term, -frequency), y=frequency)) +
  geom_bar(stat="identity", fill="orange")+ theme(axis.text.x = element_text(angle = 45,hjust=1) )
p


## First word cloud


layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, "WordCloud 1", col = "#1b98e0", cex = 2)
wordcloud(rownames(freq), freq[,1], max.words=50, colors=brewer.pal(1, "Dark2"), scale=c(3,0.25))

plot.new()
text(x=0.5, y=0.5, "WordCloud 2", col = "#1b98e0", cex = 2)
### Second Word Cloud
freq = data.frame(sort(colSums(as.matrix(words_dtm_tfidf)), decreasing=TRUE))
wordcloud(rownames(freq), freq[,1], max.words=50, colors=brewer.pal(1, "Dark2"), scale=c(3,0.25))


```

```{r}

## sentiments score for capitalism
capitalism.sent <- iconv(capitalism$lemmatized_str)
s <- get_nrc_sentiment(capitalism.sent)
head(s)

barplot(colSums(s),
        las = 2,
        col = rainbow(10),
        ylab = 'Count',
        main = 'Sentiment Scores (capitalism)')



```
<br><br><br><br>

***
## See Overall Results from Communism
```{r}
################################################ Communism Overall ############################################################

## data preprocessing
words = Corpus(VectorSource(communism$lemmatized_str))
words = tm_map(words, removeNumbers)
words = tm_map(words, removePunctuation)
words = tm_map(words, removeWords, c("the", "and", "PRON", stopwords("english"))) # Remove PRON 
words = tm_map(words, removeWords, c("must", "however", "two", "one", "upon", "much", "every", "either", "must", "can","may","therefore","will", "good","great", stopwords("english")))
words =  tm_map(words, stripWhitespace)

### Document matirx1
words_dtm <- DocumentTermMatrix(words)
### Document matirx2
words_dtm_tfidf <- DocumentTermMatrix(words, control = list(weighting = weightTfIdf))
words_dtm_tfidf = removeSparseTerms(words_dtm_tfidf, 0.95)



## creating freq data frame
freq.communism = data.frame(sort(colSums(as.matrix(words_dtm)), decreasing=TRUE))
table = data.frame(term = row.names(freq.communism), frequency= freq.communism)
colnames(table) = c('term', 'frequency')

# Bar chart
communism_chart<-ggplot(data= subset(table, frequency >800), aes(x=reorder(term, -frequency), y=frequency)) +
  geom_bar(stat="identity", fill="orange")+ theme(axis.text.x = element_text(angle = 45,hjust=1) )
communism_chart


## First word cloud

layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, "WordCloud 1", col = "#1b98e0", cex = 2)
wordcloud(rownames(freq.communism), freq.communism[,1], max.words=50, colors=brewer.pal(1, "Dark2"))

### Second Word Cloud

layout(matrix(c(1, 2), nrow=2), heights=c(1, 4))
par(mar=rep(0, 4))
plot.new()
text(x=0.5, y=0.5, "WordCloud 2", col = "#1b98e0", cex = 2)
freq.communism = data.frame(sort(colSums(as.matrix(words_dtm_tfidf)), decreasing=TRUE))
wordcloud(rownames(freq.communism), freq.communism[,1], max.words=50, colors=brewer.pal(1, "Dark2"))


```

#### Serveral key words from School of Commuism, such as labour, production, capitalist, labourer. The following is the commuist veiws on those words:

* ####  labourer.:
* ####  capitalist:
* ####  Production


#### However, in order to better understand frequency of key words, we need to split it into 3 subsets. There are 3 books introduced under communism: Communist_Manifesto, Capital, and Essential Works Of Lenin 

```{r}
################################################ Communism sentiment ############################################################
## sentiments score for communism
communism.score <- iconv(capitalism$lemmatized_str)
s <- get_nrc_sentiment(communism.score)
head(s)

communism.sent = barplot(colSums(s),
        las = 2,
        col = rainbow(10),
        ylab = 'Count',
        main = 'Sentiment Scores (communism.sent)')

communism.sent

```


<br><br><br><br>
### See Overall Results from Communism Mannifest
```{r}
################################################   Communist_Manifesto ############################################################

## data preprocessing
words = Corpus(VectorSource(Communist_Manifesto$lemmatized_str))
words = tm_map(words, removeNumbers)
words = tm_map(words, removePunctuation)
words = tm_map(words, removeWords, c("the", "and", "PRON", stopwords("english"))) # Remove PRON 
words = tm_map(words, removeWords, c("must", "however", "two", "one", "upon", "much", "every", "either", "must", "can","may","therefore","will", "good","great", stopwords("english")))
words = tm_map(words, removeWords, c("even", "always", "whole", stopwords("english"))) 
words =  tm_map(words, stripWhitespace)

### Document matirx1
words_dtm <- DocumentTermMatrix(words)
### Document matirx2
words_dtm_tfidf <- DocumentTermMatrix(words, control = list(weighting = weightTfIdf))
words_dtm_tfidf = removeSparseTerms(words_dtm_tfidf, 0.95)



## creating freq data frame
freq = data.frame(sort(colSums(as.matrix(words_dtm)), decreasing=TRUE))
table = data.frame(term = row.names(freq), frequency= freq)
colnames(table) = c('term', 'frequency')

# Bar chart
communism_chart<-ggplot(data= subset(table, frequency >30), aes(x=reorder(term, -frequency), y=frequency)) +
  geom_bar(stat="identity", fill="orange")+ theme(axis.text.x = element_text(angle = 45,hjust=1) ) + labs(x = "term")
communism_chart


## First word cloud
#par(mfrow=c(1,2))
 wordcloud(rownames(freq), freq[,1], max.words=50, colors=brewer.pal(1, "Dark2"), scale=c(3,0.25))

### Second Word Cloud
freq = data.frame(sort(colSums(as.matrix(words_dtm_tfidf)), decreasing=TRUE))
wordcloud(rownames(freq), freq[,1], max.words=50, colors=brewer.pal(1, "Dark2"), scale=c(3,0.25))


```

### class, Bourgeois, Protetariant


```{r}
################################################   Communist_Manifesto sentiments ############################################################
## sentiments score for communism
communism.score <- iconv(capitalism$lemmatized_str)
s <- get_nrc_sentiment(communism.score)
head(s)

communism.sent = barplot(colSums(s),
        las = 2,
        col = rainbow(10),
        ylab = 'Count',
        main = 'Sentiment Scores (communism.sent)')

communism.sent

```


## See Overall Results from Communism : Essential Works Of Lenin 
```{r}
################################################   Communism: Essential Works Of Lenin ############################################################

## data processing
words = Corpus(VectorSource(Lenin$lemmatized_str))
words = tm_map(words, removeNumbers)
words = tm_map(words, removePunctuation)
words = tm_map(words, removeWords, c("the", "and", "PRON", stopwords("english"))) # Remove PRON 
words = tm_map(words, removeWords, c("must", "however", "two", "one", "upon", "much", "every", "either", "must", "can","may","therefore","will", "good","great", stopwords("english")))
words =  tm_map(words, stripWhitespace)

### Document matrix1
words_dtm <- DocumentTermMatrix(words)
### Document matrix2
words_dtm_tfidf <- DocumentTermMatrix(words, control = list(weighting = weightTfIdf))
words_dtm_tfidf = removeSparseTerms(words_dtm_tfidf, 0.95)
inspect(words_dtm_tfidf[1,1:20])


## creating freq data frame
freq = data.frame(sort(colSums(as.matrix(words_dtm)), decreasing=TRUE))
table = data.frame(term = row.names(freq), frequency= freq)
colnames(table) = c('term', 'frequency')

# Bar chart
communism_chart<-ggplot(data= subset(table, frequency >1000), aes(x=reorder(term, -frequency), y=frequency)) +
  geom_bar(stat="identity", fill="orange")+ theme(axis.text.x = element_text(angle = 45,hjust=1) )
communism_chart


## First word cloud
wordcloud(rownames(freq), freq[,1], max.words=50, colors=brewer.pal(1, "Dark2"), scale=c(3,0.25))

### Second Word Cloud
freq = data.frame(sort(colSums(as.matrix(words_dtm_tfidf)), decreasing=TRUE))
wordcloud(rownames(freq), freq[,1], max.words=50, colors=brewer.pal(1, "Dark2"), scale=c(3,0.25))


```

```{r}
################################################   Communism: Essential Works Of Lenin ############################################################
## sentiments score for communism
Lenin.score <- iconv(Lenin$lemmatized_str)
s <- get_nrc_sentiment(Lenin.score)
head(s)

Lenin.score.sent = barplot(colSums(s),
        las = 2,
        col = rainbow(10),
        ylab = 'Count',
        main = 'Sentiment Scores (Lenin.score.sent)')

Lenin.score.sent

```






<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

- This is my first conclusion..


</div>


